\documentclass[12pt,a4paper]{report}

\setcounter{secnumdepth}{3} %The level of sections that get numbered
\setcounter{tocdepth}{3} %The level of sections to appear in ToC
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{braket}
\usepackage{calligra}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx} % Required for inserting images
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{aurical}
\usepackage[T1]{fontenc}

\definecolor{codegreen}{rgb}{0.133,0.545,0.133}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.827}
\definecolor{codeblue}{rgb}{0.0,0.39,0.75}
\definecolor{codeback}{rgb}{0.97,0.97,0.97}

\lstdefinestyle{python}{
  language=Python,
  backgroundcolor=\color{codeback},
  commentstyle=\color{codegreen},
  keywordstyle=\color{codeblue}\bfseries,
  stringstyle=\color{codepurple},
  numberstyle=\tiny\color{codegray},
  basicstyle=\ttfamily\small,
  breakatwhitespace=false,
  breaklines=true,
  keepspaces=true,
  numbers=left,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  xleftmargin=0pt,
  xrightmargin=0pt,
  framesep=4pt,
  frame=single,
  rulecolor=\color{codegray},
}

\begin{document}
\section{Mathematical Background}
\section{Magnetic Field Derivation}
Maxwell's equations in free space are linear \cite[p.~59]{griffiths2013} so the total magnetic field will be the sum of each individual straight line. Our main goal then, is to find the magnetic field generated at an observer point $p$ due to the current flowing along $\vec{a}$.  

We start by defining vectors $\vec{a}$, $\vec{b}$, and $\vec{c}$. 
\begin{itemize}
  \item $\vec{a}$ points along the current filament. \\
  \item $\vec{b}$ points from the observer to the end of the filament. \\
  \item $\vec{c}$ points from the observer to the start of the filament.
\end{itemize}

Note that throughout I use the convention $\left \vert \vec{a} \right \vert = a$.

Now, we use the Biot Savart Law to find the magnetic field in each of the lines. 

\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \int \frac{d\vec{l}\times \vec{r}}{r^3}  
  \label{eq:}
\end{equation}

To work out this integral we first parametrise $\vec{r}$ in time, yielding:
\begin{align*}
  \vec{r}(t) &= \vec{c} + \vec{a}t \text{, } t \in [0,1] \\
  d\vec{l} &= \vec{a}dt
\end{align*}

Substituting in gives:

\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \int_{0}^{1} \frac{(\vec{a}dt)\times (\vec{c} + \vec{a}t)}{\left \vert \vec{c} +  t\vec{a}\right\vert^3}
\end{equation}

Noting that $\vec{a} \times \vec{a} = 0$, and that $\vec{a}$ and $\vec{c}$ are constants, this simplifies to:

\begin{equation} 
  \vec{B} = \frac{\mu_0 I}{4\pi}(\vec{a} \times \vec{c}) \int_{0}^{1}  \frac{dt}{\left \vert \vec{c} +  t\vec{a}\right\vert^3}
\end{equation}

The denominator must now be simplified.
\begin{equation}
  \left\vert \vec{c} + t\vec{a} \right \vert ^3 = \left( c^2 + t^2a^2 + 2t(\vec{a}\cdot \vec{c}) \right)^{3/2}
\end{equation}

For simplicity, let $\beta = (\vec{a} \cdot \vec{c})$

\begin{equation}
  \left\vert \vec{c} + t\vec{a} \right \vert ^3 =  \left( a^2t^2 + 2\beta t + c^2  \right)^{3/2}
\end{equation}

Completing the square:

\begin{equation}
  \left\vert \vec{c} + t\vec{a} \right \vert ^3 =  a^{3} \left( \left ( t + \frac{\beta}{a^2} \right)^2 -\frac{\beta^2}{a^4} + \frac{c^2}{a^2} \right)^{3/2}
\end{equation}

Now let $u = t + \frac{\beta}{a^2}$, $du = dt$, $u(0) = \frac{\beta}{a^2}$, $u(1) = 1 + \frac{\beta}{a^2}$. Also, let $\delta = \frac{c^2}{a^2} - \frac{\beta^2}{a^4}$.

Subbing back into our Biot Savart Formula gives:

\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a} \times \vec{c}}{a^3} \int_{\frac{\beta}{a^2}}^{1+\frac{\beta}{a^2}} \frac{du}{\left(u^2 + \delta\right)^{3/2}}
\end{equation}

Want to use the identity $\sec^2\phi = 1 + \tan^2\phi$, to do so, multiply across by a factor of $\delta^{3/2}$

\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a} \times \vec{c}}{a^3\delta^{3/2}} \int_{\frac{\beta}{a^2}}^{1+\frac{\beta}{a^2}} \frac{du}{\left(\frac{u^2}{\delta} + 1 \right)^{3/2}}
\end{equation}

Now that it's in the correct form let: $\tan^2\phi = \frac{u^2}{\delta}$, then: 
\begin{align*}
  \tan\phi &= \frac{u}{\sqrt{\delta}} \\
  \sec^2\phi \, d\phi &= \frac{1}{\sqrt{\delta}} du \\
  \phi\left(\frac{\beta}{a^2}\right) &= \arctan \left( \frac{\beta}{a^2\sqrt{\delta}} \right) \\
  \phi\left( 1 + \frac{\beta}{a^2} \right) &= \arctan \left( \frac{1+\frac{\beta}{a^2}}{\sqrt{\delta}} \right)
\end{align*}

Substituting back in:
\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a} \times \vec{c}}{a^3\delta^{3/2}} \int_{\arctan\left (\frac{\beta}{a^2\sqrt{\delta}}\right)}^{\arctan\left(\frac{1}{\sqrt{\delta}}\left(1+\frac{\beta}{a^2}\right)\right)} \frac{\sqrt{\delta} \sec^2 \phi \, d\phi}{\left(1 + \tan^2\phi \right)^{3/2}}
\end{equation}

Using the identities $\sec^2 \phi = 1 + \tan^2 \phi$ and $\cos \phi = \frac{1}{\sec \phi}$ and simplifying yields:

\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a} \times \vec{c}}{a^3\delta} \int_{\arctan\left (\frac{\beta}{a^2\sqrt{\delta}}\right)}^{\arctan\left(\frac{1}{\sqrt{\delta}}\left(1+\frac{\beta}{a^2}\right)\right)} \cos\phi \, d\phi
\end{equation}

Solving:

\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a} \times \vec{c}}{a^3\delta} \left ( \sin\left( \arctan\left(\frac{1}{\sqrt{\delta}}\left(1+\frac{\beta}{a^2}\right)\right)\right) - \sin \left( \arctan\left (\frac{\beta}{a^2\sqrt{\delta}}\right) \right) \right )
\end{equation}

Now, we must consider a right angled triangle to work this out. $\sin\phi = \frac{o}{h}$, $\tan\phi = \frac{o}{a}$ therefore $\sin\left( \arctan \left( \frac{o}{a} \right) \right) = \frac{o}{\sqrt{o^2 + a^2}}$ by pythagoras.

\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a} \times \vec{c}}{a^3\delta} \left( \left( \frac{1 + \frac{\beta}{a^2}}{\sqrt{\delta + \left( 1 + \frac{\beta}{a^2} \right)^2}} \right) - \left( \frac{\beta}{\sqrt{\beta^2 + a^4 \delta}} \right)  \right) 
\end{equation}

Recalling $\delta = \frac{c^2}{a^2} - \frac{\beta^2}{a^4}$, $\beta = \vec{a} \cdot \vec{c}$, and looking at each of the denominators:
\begin{align*}
  \sqrt{\delta + \left( 1 + \frac{\beta}{a^2} \right)^2} &= \sqrt{\frac{c^2}{a^2} - \frac{\beta^2}{a^4} + 1 + 2\frac{\beta}{a^2} + \frac{\beta^2}{a^4}} \\
                             &= \sqrt{1 + \frac{c^2}{a^2} + \frac{2}{a^2} \left(\vec{a} \cdot \vec{c} \right)} \\
                             &= \frac{1}{a} \sqrt{a^2 + c^2 + 2\left(\vec{a} \cdot \vec{c}\right)} \\
                             &= \frac{1}{a} \left \vert \vec{a} + \vec{c} \right \vert \\
                             &= \frac{b}{a}
\end{align*}

\begin{align*}
  \sqrt{\beta^2 + a^4 \delta} &= \sqrt{\beta^2 + a^2c^2 - \beta^2} \\
                              &= \sqrt{a^2c^2} \\
                              &= ac
\end{align*}

Subbing into our formula for $\vec{B}$ now gives:

\begin{equation}
  \vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a}\times \vec{c}}{ac^2 - \frac{\left(\vec{a} \cdot \vec{c}\right)^2}{a}} \left( \frac{1 + \frac{\vec{a}\cdot{\vec{c}}}{a^2}}{\frac{b}{a}} - \frac{\vec{a} \cdot \vec{c}}{ac} \right)
\end{equation}

Simpifying a small bit gives:

\begin{equation}
\vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a}\times \vec{c}}{a^2c^2 - \left(\vec{a} \cdot \vec{c}\right)^2} \left( \frac{a^2 + \vec{a}\cdot\vec{c}}{b} - \frac{\vec{a} \cdot \vec{c}}{c} \right)
\end{equation}

Now, picking out these two parts and simplifying, where $\theta$ is the angle subtended by $\vec{a}$ and $\vec{c}$:
\begin{align*}
  a^2c^2 - \left( \vec{a} \cdot \vec{c} \right)^2 &= a^2c^2 - a^2c^2\cos^2(\theta) \\
                               &= a^2c^2(1 - \cos^2\theta) \\
                               &= a^2c^2\sin^2\theta \\
                               &= \left \vert \vec{a} \times \vec{c} \right \vert ^2
\end{align*}
\begin{align*}
  a^2 + \vec{a} \cdot \vec{c} &= \vec{a} \cdot \vec{a} + \vec{a} \cdot \vec{c} \\
                              &= \vec{a} \cdot \left(\vec{a} + \vec{c}\right) \\
                              &= \vec{a} \cdot \vec{b}
\end{align*}
This gives us our final form:
\begin{equation}\label{eq:biot_savart_final}
  \vec{B} = \frac{\mu_0 I}{4\pi} \frac{\vec{a} \times \vec{c}}{\left \vert \vec{a} \times \vec{c} \right \vert^2 } \left( \frac{\vec{a} \cdot \vec{b}}{b} - \frac{\vec{a} \cdot \vec{c}}{c} \right)
\end{equation}
Now, remembering that this equation is linear and that each coil is made up of straight line filaments we get:

\begin{equation}
\vec{B}_{\text{total}} = \sum_{\text{coils}} \sum_{\text{filaments}}  \vec{B}_{\text{filament}} 
\end{equation}
Now, since we are in free space we use the identity $\vec{H} = \frac{\vec{B}}{\mu_0}$ \cite[p.~285]{griffiths2013}

\section{Understanding the forward map.}
The problem is framed as an inverse problem. The forward map takes position and orientation data and calculates 8 flux values from each of the coils. Our goal is to approximate an inverse to this map. To do so, we first try to understand the forward map 
\subsection{Definition and properties.}
First we define a pose vector $\mathbf{p} \in \mathbb{R}^5$ \\
\begin{equation}
  \mathbf{p} = 
  \begin{bmatrix}
    x \\ y \\ z \\ \theta \\ \phi 
  \end{bmatrix}
\end{equation}

In actuality, $\mathbf{p}$ is restricted to a set $\Omega \subset \mathbb{R}^5$

\begin{equation}
  \Omega = \left\{
  \begin{bmatrix} x \\ y \\ z \\ \theta \\ \phi \end{bmatrix} \in \mathbb{R}^5 : 
  \begin{matrix} x \in (-0.125,0.125) \\ y \in (-0.125,0.125) \\ z \in (0,0.25) \\ \theta \in (0,\pi) \\ \phi \in [0,2\pi) \end{matrix}
  \right\}
\end{equation}

Then we define a vector of fluxes, $\mathbf{\Phi} \in \mathbb{R}^8$
\begin{equation}
  \mathbf{\Phi} = 
  \begin{bmatrix}
    \Phi_1 \\ \Phi_2 \\ \Phi_3 \\ \Phi_4 \\ \Phi_5 \\ \Phi_6 \\ \Phi_7 \\ \Phi_8 
  \end{bmatrix}
\end{equation}

Now we can write the forward map: $\mathbf{\Phi}(\mathbf{p}): \Omega \subset \mathbb{R}^5 \rightarrow \mathbb{R}^8$. More precisely,
\begin{equation}
  \Phi_i = \mathbf{H}_i(x,y,z) \cdot \hat{n}(\theta,\phi) 
\end{equation}
where $\mathbf{H}_i$ is the magnetic field calculated at $(x,y,z)$ due to coil $i$ using eqaution \eqref{eq:biot_savart_final}, and $\hat{n}(\theta,\phi)$ is the vector normal to the sensor, defined by: 

\begin{equation}
  \hat{n}(\theta,\phi) = 
  \begin{bmatrix}
    \sin\theta\cos\phi \\ \sin\theta\sin\phi \\ \cos\theta
  \end{bmatrix}
\end{equation}

Since this maps from a subset of $\mathbb{R}^5$ to $\mathbb{R}^8$ it is clear that the forward map is not surjective.

\subsection{The Jacobian}
Now that we have established that $\mathbf{\Phi}$ is not surjective we must move our attention to thinking about local invertibility rather than global. To do so we define the Jacobian:
\begin{equation}
  J(\mathbf{p}) = \frac{\partial \mathbf{\Phi}}{\partial \mathbf{p}} \in \mathbb{R}^{8\times5} \text{, } J_{i,j} = \frac{\partial \Phi_i}{\partial p_j}
  \label{eq:}
\end{equation}
Since $\mathbf{H}$ is a finite sum of Biot Savart applications it is a smooth map away from the current filaments. $\hat{n}$ is also a smooth map, therefore $\Phi$ will also be smooth away from the current filaments and the Jacobian will be well defined there.

A closed form for $\mathbf{J}$ is cumbersome find so we instead use finite differences to approximate $\mathbf{J}$

\begin{equation}
  \mathbf{J_{:,i}} \approx \frac{\mathbf{\Phi}\left(\mathbf{p} + h * \hat{e_i} \right) - \mathbf{\Phi(\mathbf{p})}}{h}
  \label{eq:}
\end{equation}
where $\hat{e}_i$ is the unit vector in the $i$th direction, and $h$ is a small real value ($h = 10^{-5}$ in our simulations).

\subsection{Local Invertibility}

As a result of the inverse function theorem \cite[Thm 9.24]{rudin1976}; where $\mathbf{J}(\mathbf{p})$ has full column rank, or equivalently, where $\mathbf{J}^\top \mathbf{J}$ is invertible $\mathbf{\Phi}$ is locally injective and has a $C^1$ local inverse in a neighbourhood of $\mathbf{\Phi(\mathbf{p})}$.

Rank deficiency therefore signals regions where the pose cannot be recovered from the flux, even locally. Full column rnak is therefore a condition for the inverse problem to be well posed.
\end{document}
