\documentclass[12pt,a4paper]{report}

\setcounter{secnumdepth}{3} %The level of sections that get numbered
\setcounter{tocdepth}{3} %The level of sections to appear in ToC
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{braket}
\usepackage{calligra}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx} % Required for inserting images
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{aurical}
\usepackage[T1]{fontenc}

\definecolor{codegreen}{rgb}{0.133,0.545,0.133}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.827}
\definecolor{codeblue}{rgb}{0.0,0.39,0.75}
\definecolor{codeback}{rgb}{0.97,0.97,0.97}

\lstdefinestyle{python}{
  language=Python,
  backgroundcolor=\color{codeback},
  commentstyle=\color{codegreen},
  keywordstyle=\color{codeblue}\bfseries,
  stringstyle=\color{codepurple},
  numberstyle=\tiny\color{codegray},
  basicstyle=\ttfamily\small,
  breakatwhitespace=false,
  breaklines=true,
  keepspaces=true,
  numbers=left,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  xleftmargin=0pt,
  xrightmargin=0pt,
  framesep=4pt,
  frame=single,
  rulecolor=\color{codegray},
}

\begin{document}
\section{Anser Simulation in Python}

We simulate the Anser system in python, developing on a MATLAB simulation by (WHO MADE IT?). Here's the pipeline:

\subsection{Coil geometry}

First we generate the vertex coordinates for a square spiral PCB emitter coil. This is done in a local coordinate system and then copies are rotated and translated to place them in the global coordinate system. 

Each coil is a square which spirals in, it has $N$ turns per layer, the sidelength of the outermost square is $l$, the trace width is $w$, there is a line to line spacing of $s$ and the thickness of the PCB is $z_{thick}$. After the coil has done $N$ turns on the upper layer, it is connected with a via to the lower layer where the coil spirals out again. 

\subsection{Conversion from Local to Global Coordiantes}

As all of the coils are the same shape, only one coil is generated, then it is copied a number of times into different places in space. This is done inside \lstinline[style=python]|local_to_global|

The module selects an axis about which the rotation takes place. This is represented as an integer $(0,1,2) - (x,y,z)$. This works nicely because the rotation matrix can be generated using an even permutation of the axes. The module then applies the permuted rotation matrix to a copy of the input vector and then applies a translation.

\subsection{Field Calculation}

The calculation of the magnetic field generated by the coils is done in \lstinline[style=python]|local_to_global|. It uses the linearity of maxwell's equations in free space to calculate the total magnetic field due to the coils at an observer point as the sum of each straight-line segment. It then implements equation \ref{eq:biot_savart_final} to calculate the magnetic field.

\subsection{Objective Function}

The objective function takes in the real observed flux, and returns the difference between it and the flux calculated using the simulation. It calculates the simulated flux as:

\begin{equation}
  \Phi = H_{sim} \cdot \hat{n}_{obs}
\end{equation}
where:
\begin{itemize}
  \item $H_{sim}$ is the simulated magnetic field 
  \item $\hat{n}_{obs}$ is the unit vector normal to the observer.
\end{itemize}

\end{document}
